### 2022-10-14 manuscript.Rmd
Add control analysis for TFR

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    epochs_dir = here(output_dir, "epochs"),
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive"),
      c("Insight/Informed", "Insight/Exclude_informed")
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 1
  )
}

@@

  # Fit the model for each component
  map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
    set_names(deps) -> models_control

@@

# Extract relevant statistics to print in the main text
map(models_control, function(mod) as_tibble(mod$anova, rownames = "effect")) %>%
  bind_rows(.id = "component") %>%
  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table_control
map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table_control
```

>>>>

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    epochs_dir = here(output_dir, "epochs"),
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      "name" = list("P1", "N170", "N400"),
      "tmin" = list(0.1, 0.15, 0.4),
      "tmax" = list(0.15, 0.2, 0.7),
      "roi" = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = c("phase/condition"),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Naive"),
      c("Insight/Informed", "Insight/Naive"),
      c("Post-insight/Informed", "Post-insight/Naive"),
      c("Insight/Informed", "Insight/Exclude_informed")
    ),
    tfr_components = list(
      name = list("alpha_beta"),
      tmin = list(0.6),
      tmax = list(1.2),
      fmin = list(8.0),
      fmax = list(20.0),
      roi = list(c("P3", "Pz", "P4", "PO3", "POz", "PO4"))
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 1
  )
}

@@

  # Fit the model for each ERP component
  map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
    set_names(deps) -> models_control

  # Fit an additional model for event-related power, controlling for RTs
  form_rt <- ~ phase * condition + log(rt) +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models_control$alpha_beta <-
    fit_mixed_models(form = form_rt, data = trials_main, dep = "alpha_beta")

@@

# Extract relevant statistics to print in the main text
map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table_control
```
